---
title: Final Project
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r libraries}
library(dplyr)
library(ggplot2)
library(tidyverse)     # for data cleaning and plotting
library(googlesheets4) # for reading googlesheet data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data       
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
library(plotly)        # for the ggplotly() - basic interactivity
library(gganimate)     # for adding animation layers to ggplots
library(gifski)        # for creating the gif (don't need to load this library every time,but need it installed)
library(transformr)    # for "tweening" (gganimate)
library(shiny)         # for creating interactive apps
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
gs4_deauth()           # To not have to authorize each time you knit.
library(mapproj)
theme_set(theme_minimal())
library(ggmap)
```



```{r}
library(readr)
mn_contrib <- read_csv("~/Desktop/Stat112/indivs_Minnesota18.csv")

zip_codes <- read_csv("~/Desktop/Stat112/zip_code_database.csv")
```


```{r}
states <- map_data("state")
mn_df <- subset(states, region == "minnesota")
counties <- map_data("county")
mn_county <- filter(counties, region == "minnesota") %>%
  select(-region) %>%
  mutate(region = subregion)
```


```{r}
main <- mn_contrib %>%
  mutate(Zip = as.numeric(Zip)) %>%
  left_join(zip_codes,
            by = "Zip") %>%
  mutate(county1 = str_to_lower(county),
         county2 = str_remove(county1, pattern = " county"),
         county2 = str_remove(county2, pattern = "\\.")) %>%
  select(-acceptable_cities, 
         -unacceptable_cities, 
         -state, 
         -decommissioned, 
         -country, 
         -world_region, 
         -area_codes, 
         -timezone, 
         -type, 
         -Microfilm, 
         -OtherID, 
         -Type, 
         -Realcode, 
         -Street, 
         -Ultorg, 
         -Contribid, 
         -Cycle, 
         -Recipcode, 
         -Source, 
         -primary_city, 
         -county, 
         -county1) %>%
  mutate(county = county2) %>%
  select(-county2) %>%
  group_by(county) %>%
  summarize(mean_amt = mean(Amount))

main %>%
  ggplot() + 
  geom_map(map = mn_county, aes(map_id = county, fill = -mean_amt)) + 
  expand_limits(x = mn_county$long, y = mn_county$lat) 
``` 


So, I tried to create a map that shows the proportion of donations amounts by gender in each county. However, I 
realized that I am not sure how to represent different percentages within one county. I just created this map 
that shows the proportion of donations amounts from women. I'll try to go to Robert's office hours tomorrow and 
ask if he knows how to include the different percentages!


```{r}
main <- mn_contrib %>%
  mutate(Zip = as.numeric(Zip)) %>%
  left_join(zip_codes,
            by = "Zip") %>%
  mutate(county1 = str_to_lower(county),
         county2 = str_remove(county1, pattern = " county"),
         county2 = str_remove(county2, pattern = "\\.")) %>%
  select(county2,
         Gender,
         Amount) %>%
  mutate(county = county2) %>%
  select(-county2) %>%
  group_by(county) %>%
  summarize(total_amount = sum(Amount))

gender_amounts <- mn_contrib %>%
  mutate(Zip = as.numeric(Zip)) %>%
  left_join(zip_codes,
            by = "Zip") %>%
  mutate(county1 = str_to_lower(county),
         county2 = str_remove(county1, pattern = " county"),
         county2 = str_remove(county2, pattern = "\\.")) %>%
  select(county2,
         Gender,
         Amount) %>%
  mutate(county = county2) %>%
  select(-county2) %>%
  group_by(county, Gender) %>%
  summarize(total_amount_gender = sum(Amount)) %>%
  filter(Gender == "F")

gender_amounts <- left_join(gender_amounts, main, by = c("county")) %>% 
  mutate(proportion_women = total_amount_gender / total_amount)

gender_amounts %>%
  ggplot() + 
  geom_map(map = mn_county, aes(map_id = county, fill = proportion_women)) + 
  expand_limits(x = mn_county$long, y = mn_county$lat) 

```

```{r}

mn_contrib %>% 
  filter(str_length(Zip) == 5) %>% 
  select(Zip) %>% 
  unique()

```


```{r}

hi <- mn_contrib %>% 
  filter(Gender == c("U", "N"))


hi


```





